---
title: "bootstrapping"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)
library(modelr)


```

simulate two datasets

```{r}
set.seed(1)

n_samp = 250

sim_df_const = 
  tibble(x = rnorm(n_samp, 1, 1),
         error = rnorm(n_samp, 0, 1),
         y = 2 + 3 * x + error
         )


sim_df_nonconst = 
  sim_df_const |> 
  mutate(
    error = 0.75 * error * x ,
    y = 2 + 3 * x + error) # the error depends on X you have. error dist depends on x in a way that violates linear regression assumption
```

look at these data

```{r}
sim_df_const |> 
  ggplot(aes(x = x, y = y)) + 
  geom_point()

sim_df_nonconst |> 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

 if you do lienar regression on non const, ur gonna get incorrect values since assumptions are violated
 
 
```{r}
sim_df_const |> 
  lm( y ~ x , data = _) |> 
  broom::tidy() |> 
  knitr::kable(digits = 3)

sim_df_nonconst |> 
  lm( y ~ x , data = _) |> 
  broom::tidy() |> 
  knitr::kable(digits = 3) 

# should be getting narrow error for intercept non const intercept, but we see same standard error for both datasets
```


write function to draw bootstrap sample


```{r}
boot_sample = function(df) {
  sample_frac(df, size = 1, replace = T) # take dataframe, give me a different sample with replace = True everytime
}


```

does function work

```{r}
sim_df_nonconst |> 
boot_sample() |> 
  ggplot(aes(x = x, y = y)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = F) +
  xlim(c(-2, 4)) +
  ylim(c(-5, 16))
```


formalizae and extract results

```{r}
boot_straps = 
  tibble(
    iter = 1:5000
  ) |> 
  mutate(
    bootstrap_sample = map(iter, \(i) boot_sample(df = sim_df_nonconst))
  )
```


check you work

```{r}
boot_straps |> 
  pull(bootstrap_sample) |> 
  nth(2) |> 
  ggplot(aes(x = x, y = y)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = F) +
  xlim(c(-2, 4)) +
  ylim(c(-5, 16))
```

actually run my analyses

```{r}
bootstrap_results =
  boot_straps |> 
  mutate(
    fits = map(bootstrap_sample, \(df) lm(y~x, data = df)),
    results = map(fits, broom::tidy)
  )
```


look at reuslts

```{r}
bootstrap_results |> 
  select(iter, results) |> 
  unnest(results) |>  # 10 diff intercepts, and 10 diff slopes
  group_by(term) |> 
  summarize(
    mean = mean(estimate),
    se = sd(estimate)
  )
  

#compare the above to kable digits = 3. see that se for slope is more than se for itnercept
```

look at these firts

distribution of estimated slopes

```{r}
bootstrap_results |> 
  select(iter, results) |> 
  unnest(results) |> 
  filter(term == "x") |> 
  ggplot(aes(x = estimate)) +
  geom_density()


bootstrap_results |> 
  select(iter, results) |> 
  unnest(results) |> 
  group_by(term) |> 
  summarise(
    ci_lower = quantile(estimate, 0.025),
    ci_upper = quantile(estimate, 0.975)
  )
```


do the same as above more consolidated

```{r}
sim_df_nonconst |> 
  bootstrap(n = 10)
```

make the dataframe
fit linear model
extract avlues

```{r}
sim_df_nonconst |> 
  bootstrap(n = 10) |> 
  mutate(
    df = map(strap, as_tibble),
    fits = map(df, \(df) lm(y ~ x, data = df)),
    results = map(fits, broom::tidy)
  ) |> 
  select(.id, results) |> 
  unnest(results)
```


look at waht this means

```{r}
bootstrap_results |> 
  group_by(term) |> 
  summarize(
    mean = mean(estimate),
    se = sd(estimate)
  )
```


# AIrbnb

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  rename(
    borough = neighbourhood_group
  ) |> 
  filter(
    borough != "Staten Island"
  ) |> 
  drop_na(price, stars, room_type) |> 
  select(price, stars, room_type, borough)
```

what does data look like

```{r}
nyc_airbnb |> 
  ggplot(aes(x = stars, y = price, color = room_type)) +
  geom_point(alpha = 0.5)
```


try to do bootstrap

hw6 q2 code is similar to this
```{r}
airbnb_bootstrap_results = 
  nyc_airbnb |> 
  filter (borough == "Manhattan") |> 
  bootstrap(n=1000) |> 
  mutate(
    df = map(strap, as_tibble),
    fits = map(df, \(df) lm(price ~ stars + room_type, data = df)),
    results = map(fits, broom::tidy)
  ) |> 
  select(.id, results) |> 
  unnest(results)
```


look at distribution of slope of stars
```{r}
airbnb_bootstrap_results |> 
  filter(term == "stars") |> 
  ggplot(aes(x = estimate)) +
  geom_density()
```

