---
title: "Cross validation"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)
library(modelr)

```

```{r}
data("lidar")
```

```{r}
lidar_df = 
  lidar |> 
  mutate(id = row_number())

lidar_df |> 
  ggplot(aes(x = range, y = logratio)) + 
  geom_point()

# see graph is non linear, and non constant variance.
```

## Create dataframes

Creating training and test dataset
```{r}
train_df = 
  sample_frac(lidar_df, size = .8) |> 
  arrange(id)

test_df = anti_join(lidar_df, train_df, by = "id")
  # rows in lidar that did not show up in testing dataframe
```

Look at training and test dataframe

```{r}
ggplot(train_df, aes(x = range, y = logratio)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

Fit a few diff models to train_df
```{r}
linear_mod = lm(logratio ~ range, data = train_df)
smooth_mod = mgcv::gam(logratio ~ s(range), data = train_df)
wiggly_mod = mgcv::gam(logratio ~ s(range, k = 50), sp = 10e-8, data = train_df)

# mgcv - non linear model
# gam - gitting non linear model
```

```{r}
train_df |> 
  add_predictions(wiggly_mod) |> 
  ggplot(aes(x = range, y = logratio)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")

# linear mod is not a good model
```

Calculate rmse

```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)

# smooth better than linear, wiggly doing too much
```

## Iterate!

```{r}
cv_df = 
  crossv_mc(lidar_df, n = 100) |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

# iterate and save as table using as_tibble
```

check this worked

```{r}
cv_df |> pull(train) |> nth(1)

# see that we have diff datasets using iterations
```


Fit model for each of the dataset

```{r}
lidar_lm = function(df) {
  
  lm(logratio ~ range, data = df)
  
}
```

```{r}
cv_df =
  cv_df |> 
  mutate(
    linear_fits = map(train, \(df) lm(logratio ~ range, data = df)),
    smooth_fits = map(train, \(df) mgcv::gam(logratio ~ s(range), data = df)),
    wiggly_fits = map(train, \(df) mgcv::gam(logratio ~ s(range, k = 50), sp = 10e-8, data = df))
  ) |> 
  mutate(
    rmse_linear = map2_dbl(linear_fits, test, rmse),
    rmse_smooth = map2_dbl(smooth_fits, test, rmse),
    rmse_wiggly = map2_dbl(wiggly_fits, test, rmse)
  )

# /df is annonymous function, embed function to the right in map
# second chunk is mapping rmse for each testing dataset for each linear model fit. map 2 because mapping across 2 columns. map2_dbl bc just want to pull out the value
```

let's look at what the baove produced

```{r}
cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) |> 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()

# see linear model is worst, best is smooth
```


## Child growth

```{r}
growth_df = 
  read_csv("data/nepalese_children.csv")
```


```{r}
growth_df |> 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .5)
```

Lets fit som emodels.
Piece wise linear model is linear but changes slopes at certain point

```{r}
growth_df =
  growth_df |> 
  mutate(
    weight_cp7 = (weight > 7) * (weight - 7)
  )

# the change point is at age 7
```

let's fit three models

```{r}
linear_mod = lm(armc ~ weight, data = growth_df)
pwl_mod    = lm(armc ~ weight + weight_cp7, data = growth_df)
smooth_mod = mgcv::gam(armc ~ s(weight), data = growth_df)
```

put the predictions on the graph

```{r}
growth_df |> 
  add_predictions(pwl_mod) |> 
  ggplot(aes(x = weight, y = armc)) +
  geom_point(alpha = .5) + 
  geom_line(aes(y = pred), color = "red")
```

now cross validate

```{r}
cv_df = 
  crossv_mc(growth_df, n = 100) |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_df = 
  cv_df |> 
  mutate(
    linear_mod = map(train, \(df) lm(armc ~ weight, data = df)),
    pwl_mod    = map(train, \(df) lm(armc ~ weight + weight_cp7, data = df)),
    smooth_mod = map(train, \(df) mgcv::gam(armc ~ s(weight), data = df))
  ) |> 
  mutate(
    rmse_linear = map2_dbl(linear_mod, test, rmse),
    rmse_pwl    = map2_dbl(pwl_mod, test, rmse),
    rmse_smooth = map2_dbl(smooth_mod, test, rmse)
  )
```

Look at the violin plots

```{r}
cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) |> 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()
```

