---
title: "linear_models"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

```{r}
data(nyc_airbnb)
```

Look at data / do some cleaning.

```{r}
nyc_airbnb = 
  nyc_airbnb |> 
  mutate(
    stars = review_scores_location / 2
  ) |> 
  rename(
    borough = neighbourhood_group
  ) |> 
  filter(borough != "Staten Island") |> 
  select(price, stars, borough, room_type, neighbourhood)
```


fit regression

borough is character variable. R converts to factor, then runs regression. It creates dummy variables for you by alphabetical order based on factor order. In this case brooklyn is the reference?

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

additional cleaning then refit

fct_infreq - put categories in order of what frequency they appear in dataset. the biggest category is first. Make reference group your biggest category for borough

```{r}
nyc_airbnb= 
  nyc_airbnb |> 
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)
  )

fit = lm(price ~ stars + borough, data = nyc_airbnb)

```

look at lm stuff

see 

```{r, eval = F}
summary(fit)
names(summary(fit))
summary(fit)[["coefficients"]]
summary(fit)[["df"]]

fitted.values(fit)
residu(fit)
```

look at cleaner `lm` stuff

```{r}
fit |> 
  broom::tidy() |> 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) |> 
  select(term, estimate, p.value) |> 
  knitr::kable(digits = 3)

fit |> 
  broom::glance()

```


## Diagnostics

look at residuals. 

Any time you fit a model have to do this

```{r}
nyc_airbnb |> 
  modelr::add_residuals(fit) |> # adds residuals to table
  modelr::add_predictions(fit) |> 
  filter(resid < 1000) |> 
  ggplot(aes(x =resid)) +
  geom_histogram()

nyc_airbnb |> 
  modelr::add_residuals(fit) |> # adds residuals to table
  modelr::add_predictions(fit) |> 
  filter(resid < 1000) |> 
  ggplot(aes(x = borough, y = resid)) +
  geom_violin()

nyc_airbnb |> 
  modelr::add_residuals(fit) |> # adds residuals to table
  modelr::add_predictions(fit) |> 
  filter(resid < 1000) |> 
  ggplot(aes(x = stars, y = resid)) +
  geom_point()
```


## Hypothesis testing

this is for individual predictors
```{r}
fit |> 
  broom::tidy()
```

but what about categorical predictor

```{r}
fit_alt = lm(price ~ stars + borough + room_type, data = nyc_airbnb)
fit_null = lm(price ~ stars + borough , data = nyc_airbnb)

anova(fit_null, fit_alt) |> 
  broom::tidy()
```

## Interactions vs nested data


```{r}
fit_interactions = 
  lm(price ~ stars + room_type * borough, data = nyc_airbnb)

fit_interactions |> 
  broom::tidy()
```
the effect of start in brooklyn is 27.1-6.14


Lets just look at brooklyn first
```{r}
nyc_airbnb |> 
  filter(borough == "Brooklyn") |> 
  lm(price ~ stars + room_type, data = _) |> 
  broom::tidy()

nyc_airbnb |> 
  filter(borough == "Manhattan") |> 
  lm(price ~ stars + room_type, data = _) |> 
  broom::tidy()

nyc_airbnb |> 
  filter(borough == "Bronx") |> 
  lm(price ~ stars + room_type, data = _) |> 
  broom::tidy()

nyc_airbnb |> 
  filter(borough == "Queens") |> 
  lm(price ~ stars + room_type, data = _) |> 
  broom::tidy()
```


start here for homework problem
write a short function to do the above

```{r}
lm_airbnb = function(df) {
  
  lm(price ~ stars + room_type, data = df)
}

nyc_airbnb |> 
  filter(borough == "Queens") |> 
  lm_airbnb() |> 
  broom::tidy()
```

Create a list of dataframes, and iterate to fit the model each time

```{r}
nested_lm_results = 
  nyc_airbnb |> 
  nest(data = -borough) |> 
  mutate(
    fits = map(data, lm_airbnb),
    results = map(fits, broom::tidy)
  ) |> 
  select(borough, results) |> 
  unnest(results)

```



do some untidying

below, we don't get p values but see the difference between boroughs for exploratory analysis

```{r}
nested_lm_results |> 
  select(borough, term, estimate) |> 
  pivot_wider(
    names_from = term, 
    values_from = estimate
  )
  
```


use an *anonymous* function instead of `lm_airbnb`

the backslash thing is to allow you to not need to have the function on the side

```{r}
nested_lm_results = 
  nyc_airbnb |> 
  nest(data = -borough) |> 
  mutate(
    fits = map(data, \(df) lm(price ~ stars + room_type, data = df)), 
    results = map(fits, broom::tidy)
  ) |> 
  select(borough, results) |> 
  unnest(results)
```



let's do an even more extreme example

effect of stars in different neighborhoods
```{r}
manhattan_analysis = 
  nyc_airbnb |> 
  filter(
    borough == "Manhattan"
  ) |> 
  nest(data = -neighbourhood) |> 
  mutate(
    fits = map(data, \(df) lm(price ~ stars + room_type, data = df)),
    results = map(fits, broom::tidy)
  ) |> 
  select(neighbourhood, results) |> 
  unnest(results)
```

Make a plot

effect of increasing start values across neihgborhoods in manhattan

```{r}
manhattan_analysis |> 
  filter(term == "stars") |> 
  mutate(
    neighbourhood = fct_reorder(neighbourhood, estimate)
  ) |> 
  ggplot(aes(x = neighbourhood, y = estimate)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

