---
title: "linear_models"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

```{r}
data(nyc_airbnb)
```

Look at data / do some cleaning.

```{r}
nyc_airbnb = 
  nyc_airbnb |> 
  mutate(
    stars = review_scores_location / 2
  ) |> 
  rename(
    borough = neighbourhood_group
  ) |> 
  filter(borough != "Staten Island") |> 
  select(price, stars, borough, room_type, neighbourhood)
```


fit regression

borough is character variable. R converts to factor, then runs regression. It creates dummy variables for you by alphabetical order based on factor order. In this case brooklyn is the reference?

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

additional cleaning then refit

fct_infreq - put categories in order of what frequency they appear in dataset. the biggest category is first. Make reference group your biggest category for borough

```{r}
nyc_airbnb= 
  nyc_airbnb |> 
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)
  )

fit = lm(price ~ stars + borough, data = nyc_airbnb)

```

look at lm stuff

see 

```{r, eval = F}
summary(fit)
names(summary(fit))
summary(fit)[["coefficients"]]
summary(fit)[["df"]]

fitted.values(fit)
```

look at cleaner `lm` stuff

```{r}
fit |> 
  broom::tidy() |> 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) |> 
  select(term, estimate, p.value) |> 
  knitr::kable(digits = 3)

fit |> 
  broom::glance()

```










